The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-05 src/ms.tex
Add another missing hyphen

The Cherenkov Telescope (CTA) will be the next generation very-high-energy
gamma-ray observatory.
CTA will improve over the current generation of imaging atmospheric Cherenkov telescopes (IACTs)
by a factor of five to ten in sensitivity and will be able to observe the whole sky from a combination of two sites:
a northern site in La Palma, Spain, and a southern one in Paranal, Chile.
CTA will be able to observe gamma rays in a broad energy range from around $20\,\mathrm{GeV}$ to over $300\,\mathrm{TeV}$
using three different types of telescopes. In total over 100 telescopes are planned at the two sites.
CTA will also be the first open gamma-ray observatory.

@@

The
\href{https://github.com/astropy/astropy-project/blob/main/roadmap/roadmap.md}{Astropy Roadmap} is a document in the \texttt{astropy-project} \github
repository within the \astropy organization that captures high level actionable
items that the Astropy project aims to undertake to improve the health and
stability of the project. It is a static document that is revisited regularly at
the Astropy coordination meetings, intended to keep track of progress and write
new versions as needed. There is a related project board linked to the Roadmap
document that holds specific issues and efforts related to Roadmap items. The
project board is a living document that is continually updated as work is
planned, assigned, and completed.

>>>>

The Cherenkov Telescope (CTA) will be the next generation very-high-energy
gamma-ray observatory.
CTA will improve over the current generation of imaging atmospheric Cherenkov telescopes (IACTs)
by a factor of five to ten in sensitivity and will be able to observe the whole sky from a combination of two sites:
a northern site in La Palma, Spain, and a southern one in Paranal, Chile.
CTA will be able to observe gamma rays in a broad energy range from around $20\,\mathrm{GeV}$ to over $300\,\mathrm{TeV}$
using three different types of telescopes, in total over 100 telescopes are planned at the two sites.
CTA will also be the first open gamma-ray observatory.

@@

The
\href{https://github.com/astropy/astropy-project/blob/main/roadmap/roadmap.md}{Astropy Roadmap} is a document in the \texttt{astropy-project} \github
repository within the \astropy organization that captures high-level actionable
items that the Astropy project aims to undertake to improve the health and
stability of the project. It is a static document that is revisited regularly at
the Astropy coordination meetings, intended to keep track of progress and write
new versions as needed. There is a related project board linked to the Roadmap
document that holds specific issues and efforts related to Roadmap items. The
project board is a living document that is continually updated as work is
planned, assigned, and completed.
